%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\renewcommand{\labelitemii}{$\diamond$}
\renewcommand{\labelitemiii}{$-$}

\name{Aaron Maurer} % Your name
\address{610~$\cdot$~717~$\cdot$~8858 \\ ajmaurer89@gmail.com} % Your phone number and email
\address{www.github.com/ajmaurer}
\address{1267 Page St, Apt F \\ San Francisco, CA 94117}

\begin{document}

%----------------------------------------------------------------------------------------
%	Objective
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
I am an experienced statistician and data scientist with a zeal for answering hard questions with big data. After spending three years analyzing huge Medicare data sets at Acumen LLC, I went back to get my Master's in Statistics. Now I'm looking for a company that could use my help gaining insights and predictions from its data. 

{\bf Specialties:} Nonparametric, Bayesian, and Classical Statistics; Large Scale Data Mining; Machine Learning; Regression Analysis; Mathematical Optimization; Econometric Modeling

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programing Languages 	& Python, Stata, SAS, R, SQL, Visual Basic, Some MATLAB \\
Programing Tools   	    & Apache Spark, AWS EC2, MapReduce, \LaTeX, Git, SVN \\

\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    {\bf Masters of Science in Statistics} \hfill {\em Expected August 2015} \\
    University of Chicago - Chicago, Illinois \\
    Thesis: {\em Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate} \\
    Selected Coursework: Machine Learning and Large-Scale Data Analysis, Bayesian Analysis, Nonparametric Inference, Convex Optimization, Mathematical Statistics, Generalized Linear Regression


    {\bf Bachelor of Arts in Mathematics \& History, Cum Laude} \hfill {\em June 2011} \\ 
    Carleton College - Northfield, Minnesota  \\
    Distinction in the Math Major, Sigma Xi, Varsity Football \& Track
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

%----------------------------------------------
\vspace{0.2em}

{\bf Acumen, LLC} \hfill Burlingame, CA \\
{\em Policy Associate} \hfill {\em August 2011 - August 2014} \vspace{0.3em} 
\vspace{-0.2em}
\begin{itemize} \itemsep -0.2em
    \item Provided analytical and programing expertise to federal agencies studying healthcare  topics.
	\item Cleaned huge Medicare data sets, complied statistics, and built statistical models in Stata and SAS to provide prediction or inference for these studies.
    \item Worked with federal clients to develop analysis and explicate results; produced data visualization and documentation to assist client understanding. 
    \item Project work included:
    \begin{itemize} \itemsep -0.2em
    	\item {\bf \em Market and Enrollment Projections of the Affordable Care 		Act}
        \begin{itemize} \itemsep -0.2em
    		\item Developed microsimulation model to estimate ACA's effect on each individual. 	
            \item Employed series of probit regressions on person level variables to predict future enrollment. 
            \item Forecast federal budget implications, guiding \$25 billion in federal spending.
    	\end{itemize}
    	\item {\bf \em Flu Vaccine Comparative Effectiveness}
        \begin{itemize} \itemsep -0.2em
            \item Studying vaccine effectiveness presented difficulty due to distinct populations receiving the vaccine, outcome mismeasurment, and the variable latent infection risk. 
    		\item Carefully designed comparable test and control cohorts from Medicare enrollees.
            \item Implemented and tested a number of regression models to account for remaining issues, including proportional hazard and measurement error models. 
    	\end{itemize}

    	\item {\bf \em Financial Projections of Policy Reform}
        \begin{itemize} \itemsep -0.2em
    		\item Projected budget impact of Bipartisan Policy Center Medicare reform program.
            \item Developed a log-normal mixture model to simulate beneficiary level expenditures.
            \item Total net cost forecasts included in final report on the Domenici-Rivlin plan
    	\end{itemize}
        \item {\bf \em Active Surveillance of Flu Vaccine Safety}
        \begin{itemize} \itemsep -0.2em
        	\item Tracked approximately 15 million yearly vaccinations in Medicare population for cases of Guillain-Barre syndrome.
            \item Employed sequential probability test to signal when hazard was above historical levels as quickly as possible.
        \end{itemize}
    \end{itemize}
\end{itemize}
\end{rSection}

\vspace{0.4em}
%----------------------------------------------------------------------------------------
%   Selected Projects	
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Selected Projects}
    \begin{itemize}
        \item Used City of Chicago crime database to estimate weather's effect on citywide number of robberies.
            \begin{itemize} 
                \item Implemented Kernel and Poisson regressions on hourly crime counts across three years in R.
                \item Models estimated change in robbery rate with temperature by hour and day of week.
            \end{itemize}
        \item Employed Bayesian Latent Dirichlet Allocation model to categorize Wikipedia articles by topics.
            \begin{itemize} 
                \item Utilized python Onlineldavb package to download and parse $12,\!800$ random articles on which to estimate topic posterior distributions.   
                \item Using topic weighting as a low dimensional representation of each article, fit k-medians \\clustering to group similar articles.
            \end{itemize}
        \item Built L2 regularized logistic regression model to predict sentiment across $1.5$ million tweets.
            \begin{itemize} 
                \item Parsed tweets into $4,\!000$ word/emoticon feature vector in parallel using pyspark.
                \item Fit model with stochastic gradient descent, choosing optimal parameters via cross validation.
            \end{itemize}
        \item Created models to predict overall review score for RateBeer.com reviews based on description.
            \begin{itemize} 
                \item Built feature vector of tf-idf statistics of hashed words over 3 million review corpus.
                \item Fit both random forest and gradient boosted trees using Spark MLLib on AWS EC2.
            \end{itemize}

    \end{itemize} 
\end{rSection}



%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
\begin{itemize}
    \item W. Baird, A. Beveridge, A. Bonato, P. Codenotti, J. MacCauley, A. Maurer, S. Valeva, ``On the minimal order of k-cop-win graphs", {\em Contributions to Discrete Mathematics}, Vol. 9, No. 1 (2014), pp. 1-15 
    \item Hector Izurieta et al., ``Comparative effectiveness of high-dose versus standard-dose influenza vaccines in US residents aged 65 years and older from 2012 to 2013 using Medicare data: a retrospective cohort analysis", {\em The Lancet}, Vol 15, No. 3 (2015), pp. 293-300 
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%   Misc	
%----------------------------------------------------------------------------------------

\begin{rSection}{Miscellaneous/Personal} 
    Erdos Number of 3; has or will soon visit all but 4 of continuous 48 states; expert on Byzantine military history; former member of International Brotherhood of Teamsters; avid board game player 
\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
