%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\renewcommand{\labelitemii}{$\diamond$}
\renewcommand{\labelitemiii}{$-$}

\name{Aaron Maurer} % Your name
\address{Statistics Department Applicant} % Your address
\address{Fall, 2014} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	Objective
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
Quantitative researcher with a zeal for using statistical and econometric modeling to answer hard questions with big data. Looking for difficult problems to solve through thorough and thoughtful analysis.

{\bf Specialties:} Regression Analysis, Statistics, Econometric Models, Graph Theory, \\ Microsimulation, Statistical Programming
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%----------------------------------------------
\vspace{0.2em}

{\bf Acumen, LLC} \hfill Burlingame, CA \\
{\em Data and Policy Analyst} \hfill {\em August 2011 - Present} \vspace{0.3em} \\
Worked closely with various federal agencies answering empirical questions using healthcare data.
\vspace{-0.2em}
\begin{itemize} \itemsep -0.2em
	\item Preformed data mining on large Medicare and Medicaid data sets.
    \item Built statistical and econometric models.
    \item Developed statistical graphics to visualize trends in data.
    \item Worked with clients to include subject specific knowledge into analysis and explicate results.
    \item Selected Projects include:
    \begin{itemize} \itemsep -0.2em
    	\item {\bf \em Market and Enrollment Projections of the Affordable Care 		Act}
        \begin{itemize} \itemsep -0.2em
    		\item Developed microsimulation model that calculated affects of the law on a person level basis. 	
            \item Employed multiple regression models to impute insurance takeup in novel circumstances. 
            \item Predictions used to dictate spending of \$25 billion federal program.
    	\end{itemize}
    	\item {\bf \em Flu Vaccine Comparative Effectiveness}
        \begin{itemize} \itemsep -0.2em
    		\item Carefully designed a test and control sample to mitigate exogenous confounding factors.
            \item Implemented and tested several regression models to measure effectiveness while controlling for other independent factors, varying hazard, and mis-measurement of outcome.
            \item Results and novel approach in process of publication.
    	\end{itemize}
    	\item {\bf \em Financial Projections of Policy Reform}
        \begin{itemize} \itemsep -0.2em
    		\item Projected budget impact of Bipartisan Policy Center Medicare reform program.
            \item Developed model for beneficiary level expenditures under numerous policy changes.
            \item Bottom line estimates included in final report on the Domenici-Rivlin Plan
    	\end{itemize}
        \item {\bf \em Active Surveillance of Flu Vaccine Safety}
        \begin{itemize} \itemsep -0.2em
        	\item Tracked approximately 15 million yearly vaccinations in Medicare population.
        	\item Provided FDA with an estimate of post vaccination hazard of Guillain-Barre syndrome.
            \item Employed sequential probability test to signal when hazzard above historical levels.
        \end{itemize}
    \end{itemize}
\end{itemize}

%\vspace{-0.2em}
%\begin{itemize} \itemsep -0.2em
%	\item Carried out data mining on a series of large and varied data sets from Medicare and Medicaid programs.
%    \begin{itemize} \itemsep -0.2em
%    	\item Worked with information from breadth of a nearly petabyte sized database.
%        \item Conducted verification and imputation for often missing and incomplete data. 
%	\end{itemize}    
%	\item Tailored regression and statistical models to address unique problems.
%    \begin{itemize} \itemsep -0.2em
%    	\item Built flu vaccine efficacy models that adjusted for 			mismeasurement and varying hazard.
%        \item Results and methodology from several studies are being published.
%    \end{itemize}
%	\item Developed and programed econometric simulations to project novel policy scenarios.
%	\begin{itemize} \itemsep -0.2em
%		\item Developed a microsimulation model to predict the effects of the Affordable Care Act.
%        \item Model was used to allocate spending for a ten billion dollar federal program.
%		\item Created projections of a comprehensive Medicare reform plan for a major think tank.
%	\end{itemize}
%    \item Coded models and queried data to conduct surveillance in real time.
%    	\begin{itemize} \itemsep -0.2em
%        \item Tracked safety of 15 million flu vaccines yearly as a key component of the federal vaccine program.
%		\item Employed sophisticated sequential probability test to 		detect increased risk in minimum time despite data 				incompleteness and delay.
%	\end{itemize}
%	\item Worked with stakeholders to build their intution into 		analyses as well as explain results and methods.
%    	\begin{itemize} \itemsep -0.2em
%    	\item Successfully explained complicated statistical concepts and results for non-technical clients. 
%    \end{itemize}
%    \item Developed statistical graphics to visualize trends in data.

%\end{itemize}

\vspace{0.4em}
\newpage

%----------------------------------------------

{\bf The Institute for Mathematics and its Applications} \hfill Minneapolis, MN \\
{\em Undergraduate Researcher} \hfill {\em June 2010 -– July 2010} \vspace{0.3em} \\
Researched outstanding graph theoretic problems under mathematics and computer science professors. 
\begin{itemize} \itemsep -0.2em
	\item Proved novel results about pursuit evasion games.
	\begin{itemize} \itemsep -0.2em
		\item Gave talk on work at the Joint Mathematics Meeting.
	\end{itemize}
	\item Helped program algorithm to classify graphs with respect to games of cops and robbers.
\end{itemize}

\vspace{0.4em}

%----------------------------------------------


{\bf Carleton College} \hfill Northfield, MN \\
{\em Mathematics Department Assistant System Administrator} \hfill {\em June 2009 –- June 2011} \vspace{0.3em} \\
Helped administer computer systems and labs for the mathematics and computer science departments. 
\begin{itemize} \itemsep -0.2em
	\item Helped maintain Windows, Mac, and Linux machines.
\end{itemize}

\vspace{0.4em}

{\em Mathematics Skill Center Tutor} \hfill {\em March 2009 –- June 2009} \vspace{0.3em} \\
Assisted other students with mathematical skills and homework sets.
\begin{itemize} \itemsep -0.2em
	\item Tutored Calculus, Linear Algebra, Probability, and Statistics
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Carleton College} - Northfield, Minnesota \hfill {\em June 2011} \\ 
B.A. in Mathematics \& History, Cum Laude \\
Distinction in the Math Major \\
Sigma Xi\\
Varsity Football and Track \& Field
\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Analytic and Programming Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Statistical Packages 	& Stata, SAS, R, S-PLUS \\
Programing Languages 	& Python, SQL, Visual Basic, \LaTeX \\
Operating Systems 		& Windows, Linux, Mac OS \\
Mathematical Areas      & Combinatorics, Graph Theory, Probability\\
Statistical Methods		& Regression Analysis, Monte Carlo Simulation, Maximum Likelihood      

\end{tabular}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\end{rSection}

\begin{rSection}{Publications}
\begin{itemize}
	\item W. Baird, A. Beveridge, A. Bonato, P. Codenotti, J. MacCauley, A. Maurer, S. Valeva, {\em On the minimal order of k-cop-win 	graphs}, submitted to Contributions to Discrete Mathematics
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------

\begin{rSection}{Talks}
\begin{itemize}
	\item A. Maurer, J. MacCauley, S. Valeva, {\em Cops and Robbers on Planar Graphs}, 2011 Joint Mathematics Meeting, New Orleans, LA 	(January 2011)

	\item H. Izurieta, N. Thadani, Y. Lu, R. Franks, T. MaCurdy,  D. Pratt, A. Maurer, C. Worrall, H. Hong, J. Kelman, {\em Comparative effectiveness of high- versus standard-dose influenza vaccines among US residents aged 65 years and older: Preliminary results}, 7th Vaccine \& IVS Congress, Barcelona, Spain (October 2013)
    \end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}